Blocking-resistant communication\\through domain fronting

### 2014-07-31 docs/meek.tex
Edits.

The components of the system are shown in Figure~\ref{fig:architecture}.
The parts that are new in \meek
are the programs \meekclient\ and \meekserver,
which are the pluggable-transports~\cite{pt} interface between Tor and \meek.
% All the programs are free software, naturally,
% and may be downloaded from the \meek\ home page at
% \url{https://trac.torproject.org/projects/tor/wiki/doc/meek}.

@@

\subsection{Packet length}

@@

% Prevalence of no SNI.

The key idea of meek is domain fronting,
but its HTTPS tunnel has independent utility.
Another idea for deployment is to use
thousands of simple HTTP reflectors on cheap web hosting
(in place of domain fronting on a big CDN).
The request-reflecting role of a CDN could
be played by a PHP script, for example,
or a special web server configuration.
Their URLs unprotected by domain fronting,
each reflector would be easily blockable,
so there would need to be sufficiently many that
a censor could not block them all.
This deployment model is essentially the same as with
ordinary Tor bridges: have lots of volunteer-operated bridges
and make it hard to enumerate them all.
The advantage that an HTTP transport would have
is that it is easier for a volunteer to upload a PHP file to a web host
than to set up and maintain a Tor bridge.

@@

We are running a paid instance of the web app on App Engine for use by the public.
The cost for bandwidth on App Engine is \$0.12 per gigabyte,
with one gigabyte free each day.
The total cost has so far been \$1.11, with bills of
\$0.09 in March,
\$0.73 in April,
and \$0.29 in the first half of May.

\meek\ has a home page at
\url{https://trac.torproject.org/projects/tor/wiki/doc/meek}.
Our source code is in the Git repository at
\url{https://git.torproject.org/pluggable-transports/meek.git}.
As of version 0.5 (May~7, 2014), the source code consists of
about 800 lines of Go for the client programs,
400 lines for \meekserver, and
100 lines for the reflector web app.
Each of the browser extensions
(one for Firefox, one for Chrome)
is about 300 lines of JavaScript.

\subsection{Other deployment scenarios}
\label{sec:otherdeployment}

% Dreamhost? Other HTTPS webhosts with PHP bridge?

% Psiphon idea: use long-polling for downstream data.
% Works with CDNs, not with App Engine.
% Alternative techniques for push-like behavior,
% such as HTTP long polling,
% don't work well with App Engine,
% because App Engine requires requests to finish within 60 seconds.

% App Engine works when appspot.com is blocked but google.com is not.

@@

>>>>

The components of the system are shown in Figure~\ref{fig:architecture}.
The parts that are new in \meek
are the programs \meekclient\ and \meekserver,
which are the pluggable-transports~\cite{pt} interface between Tor and \meek.

@@

\subsection{Packet lengths}

@@

The key idea of meek is domain fronting,
but its HTTP-tunneling ability is useful on its own.
Another idea for deployment is to use
thousands of simple HTTP reflectors on cheap web hosting
(in place of domain fronting on a big CDN).
The request-reflecting role of a CDN could
be played by a PHP script, for example,
or a special web server configuration.
Their URLs unprotected by domain fronting,
each reflector would be easily blockable,
so there would need to be sufficiently many that
a censor could not block them all.
This deployment model is essentially the same as with
ordinary Tor bridges: have lots of volunteer-operated bridges
and make it hard to enumerate them all.
The advantage that an HTTP transport would have
is that it is easier for a volunteer to upload a PHP file to a web host
than to set up and maintain a Tor bridge.

The ``domainless'' fronting style, which omits SNI,
is useful when there is no good front domain known for a web service.
At least one CDN, Fastly, requires the domainless style.
All current web browsers support SNI,
so it is possible that lack of SNI could be used as a distinguisher.
According to our communication with
a representative of the International Computer Science Institute's
certificate notary~\cite{icsi-notary},
which observes on the order of 50~million TLS connections daily,
83.5\% of connections used SNI in June~2014.
There are apparently enough connections without SNI
that a censor will at least have to consider seriously
the costs and benefits before deciding to block SNI outright.

@@

We are running a paid instance of the web app on App Engine for use by the public.
% The cost for bandwidth on App Engine is \$0.12 per gigabyte,
% with one gigabyte free each day.
% The total cost has so far been \$1.11, with bills of
% \$0.09 in March,
% \$0.73 in April,
% and \$0.29 in the first half of May.

@@

\section{Summary}
\label{sec:summary}

We have presented domain fronting,
an HTTPS technique that uses different domain names
at different communication layers in
order to hide the remote endpoint of a communication.
We implemented meek,
a pluggable transport for Tor,
show that it resists common methods of blocking,
and begin an investigation into its
resistance against more subtle and expensive means of traffic analysis.
We discuss the results of an initial deployment of meek
in both Tor and Psiphon.

\meek\ has a home page at
\url{https://trac.torproject.org/projects/tor/wiki/doc/meek}.
Our source code is in the Git repository at
\url{https://git.torproject.org/pluggable-transports/meek.git}.
All our programs are free software.
% As of version 0.9 (June~19, 2014), the source code consists of
% about 1,100 lines of Go for the client programs,
% 400 lines for \meekserver, and
% 100 lines for the reflector application for App Engine.
% Each of the browser extensions
% (one for Firefox, one for Chrome)
% is about 400 lines of JavaScript.
